---
title: "code"
author: "Chenxi Yang, Yi Tang"
date: "15/04/2020"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)
```

# COVID-19 virus infections

From 1.22.2020 to 4.11.2020
Data came form https://www.kaggle.com/c/covid19-global-forecasting-week-4/data COVID19 Global Forecasting (Week 4)

```{r}
# read data
data<-read.csv("train.csv",header = T)
```

```{r}
# call library
library(dplyr)
library(forecast)
library(MLmetrics)
library(splines)
```

### Overall

```{r}
# summary of data
summary(data)
```

No NA in Country_Region,Date, ConfirmedCases and Fatalities.


```{r}
# number of countries or regions 
length(levels(data$Country_Region))
```

```{r}
# number of dates
length(levels(data$Date))
```


```{r}
# combine Country_Region and Province_State
data$Country_Region_Province_State<-as.factor(paste(data$Country_Region,"(",
                                    data$Province_State,")"))
head(data)
```

Only use Canada data.

```{r}
#filter Canada data
data_canada<-filter(data,Country_Region=="Canada")
data_canada$Province_State<-as.factor(as.character(data_canada$Province_State))
data_canada$Country_Region_Province_State<-
  as.factor(as.character(data_canada$Country_Region_Province_State))
head(data_canada)
```

```{r}
# summary of canada data
summary(data_canada)
```

```{r fig.width=6,fig.height=4}
# Time Series of Confirmed Cases in Canda From 2020-01.22 to 2020.04.11
province<-data_canada %>%
  group_split(Province_State)
province_name<-numeric(12)
for (i in 1:12){
    assign(paste0("province",i),as.ts(province[[i]]$ConfirmedCases))
    province_name[i]<-as.character(province[[i]]$Province_State[1])
}
color<-rainbow(12)
par(cex.main = 0.8)
ts.plot(province1,province2,province3,province4,
        province5,province6,province7,province8,
        province9,province10,province11,province12, 
        col = color,
        main="Time Series of Confirmed Cases in Canda From 2020.01.22 to 2020.04.11")
legend("topleft", legend=province_name,lty=1, col=color,cex=0.5)
```

```{r fig.width=6,fig.height=4}
# Time Series of Fatalities in Canda From 2020.01.22 to 2020.04.11
province<-data_canada %>%
  group_split(Province_State)
province_name<-numeric(12)
for (i in 1:12){
    assign(paste0("province",i),as.ts(province[[i]]$Fatalities))
    province_name[i]<-as.character(province[[i]]$Province_State[1])
}
# plot every provinces on the same plot
color<-rainbow(12)
par(cex.main = 0.8)
ts.plot(province1,province2,province3,province4,
        province5,province6,province7,province8,
        province9,province10,province11,province12, 
        col = color,
        main="Time Series of Fatalities in Canda From 2020.01.22 to 2020.04.11")
legend("topleft", legend=province_name,lty=1, col=color,cex=0.5)
```

```{r}
# convert to date variable
data_canada$Date<-as.Date(data_canada$Date, format = "%Y-%m-%d")
```

```{r}
# days after first Confirmed case happened 
case1<-function(province) {
  case_dates<-filter(data_canada, 
                     Province_State == province & ConfirmedCases > 0)
  if(nrow(case_dates) > 0) {
    return(min(case_dates$Date))
  } else {
    return(0)
  }
}
data_canada$days_after_first_confirmedCases<-0
for (i in 1:nrow(data_canada)){
  case1date<-case1(data_canada$Province_State[i])
  if(case1date != 0 && case1date <= data_canada$Date[i] ){
    data_canada$days_after_first_confirmedCases[i]<-as.numeric(data_canada$Date[i]-case1date)+1
  }
}
# avoid error for log, set 1 in days_after_first_confirmedCases if date before first confirmedCases case happened

data_canada$days_after_first_confirmedCases<-data_canada$days_after_first_confirmedCases+1
```

```{r}
# days after first Fatalities case happened
case1<-function(province) {
  case_dates<-filter(data_canada, 
                     Province_State == province & Fatalities > 0)
  if(nrow(case_dates) > 0) {
    return(min(case_dates$Date))
  } else {
    return(0)
  }
}
data_canada$days_after_first_fatalities<-0
for (i in 1:nrow(data_canada)){
  case1date<-case1(data_canada$Province_State[i])
  if(case1date != 0 && case1date <= data_canada$Date[i] ){
    data_canada$days_after_first_fatalities[i]<-as.numeric(data_canada$Date[i]-case1date)+1
  }
}
# avoid error for log, set 1 in days_after_first_fatalities if date before first fatalities case happened
data_canada$days_after_first_fatalities<-data_canada$days_after_first_fatalities+1 
```

Training data: 2020-01.22-2020.03.31
Testing data: 2020-04.01-2020.04.11

```{r}
# separate training data and testing data
train_canada<-filter(data_canada,Date<"2020-04-01")
test_canada<-filter(data_canada,Date>="2020-04-01")
```

### choosing methods: fit and check models

```{r}
# build a table
mse_dataframe<-data.frame("model"=numeric(15),
                          "per_province"=numeric(15),
                          "ConfirmedCases_mse"=numeric(15),
                          "Fatalities_mse"=numeric(15))
```

```{r}
mse_by_province_canada<-function(modelname,datatype){
  province_name<-as.character(unique(data_canada$Province_State))
  mse_total<-0
  for (i in 1:12){
    province_train<-filter(train_canada,Province_State==province_name[i])
    province_test<-filter(test_canada,Province_State==province_name[i])
    mse<-modelname(province_train,province_test,datatype)
    mse_total<-mse_total+mse
  }
  mse<-mse_total/length(province_name)
  return(round(mse,2))
}
```

#### quasipoisson logistic regression:

poisson regression used for count data, since lack of significant parameters, using quasipoisson regression to expand standard error.
```{r}
# quasipoisson regression 
mod1<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    ytrue<-testdata[,5]
    mod<-glm(traindata$ConfirmedCases~days_after_first_confirmedCases+Province_State,data=traindata,family=quasipoisson(link="log"))
  }else if(datatype=="fatalities"){
    ytrue<-testdata[,6]
    mod<-glm(traindata$Fatalities~days_after_first_fatalities+Province_State,data=traindata,family=quasipoisson(link="log"))
  }
  pred<-round(predict(mod, newdata=testdata, type = "response"),0)
  mse<-MSE(y_pred=pred, y_true=ytrue)
  return(round(mse,2))
}
```

#### quasipoisson logistic regression with log(x):

```{r}
# quasipoisson logistic regression with log(x)
mod2<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    ytrue<-testdata[,5]
    mod<-glm(traindata$ConfirmedCases~log(days_after_first_confirmedCases)+
                   Province_State,data=traindata,family=quasipoisson(link="log"))
  }else if(datatype=="fatalities"){
    ytrue<-testdata[,6]
    mod<-glm(traindata$Fatalities~log(days_after_first_fatalities)+
                   Province_State,data=traindata,family=quasipoisson(link="log"))
  }
  pred<-round(predict(mod, newdata=testdata, type = "response"),0)
  mse<-MSE(y_pred=pred, y_true=ytrue)
  return(round(mse,2))
}

```

#### 2nd degree quasipoisson polynomial regression: 

```{r}
# 2nd degree quasipoisson polynomial regression 
mod3<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    ytrue<-testdata[,5]
    mod<-glm(traindata$ConfirmedCases~
                  days_after_first_confirmedCases +
                  I(days_after_first_confirmedCases^2),
                 data=traindata,family=quasipoisson(link="log"))
  }else if(datatype=="fatalities"){
    ytrue<-testdata[,6]
    mod<-glm(traindata$Fatalities~
                 days_after_first_fatalities+
                 I(days_after_first_fatalities^2),
                 data=traindata,family=quasipoisson(link="log"))
  }
  pred<-round(predict(mod, newdata=testdata, type = "response"),0)
  mse<-MSE(y_pred=pred, y_true=ytrue)
  return(mse)
}
```

#### 3rd degree quasipoisson polynomial regression: 

```{r}
# 3rd degree quasipoisson polynomial regression 
mod4<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    ytrue<-testdata[,5]
    mod<-glm(traindata$ConfirmedCases~
                  days_after_first_confirmedCases +
                  I(days_after_first_confirmedCases^2)+
                  I(days_after_first_confirmedCases^3),
                 data=traindata,family=quasipoisson(link="log"))
  }else if(datatype=="fatalities"){
    ytrue<-testdata[,6]
    mod<-glm(traindata$Fatalities~
                 days_after_first_fatalities+
                 I(days_after_first_fatalities^2)+
                 I(days_after_first_fatalities^3),
                 data=traindata,family=quasipoisson(link="log"))
  }
  pred<-round(predict(mod, newdata=testdata, type = "response"),0)
  mse<-MSE(y_pred=pred, y_true=ytrue)
  return(mse)
}
```

#### 2nd degree quasipoisson polynomial regression with truncated splines:

```{r}
# 2nd degree quasipoisson polynomial regression with truncated splines 
tr.pwr<-function(x,knot,degree){ 
  (x>knot)*(x-knot)^degree
}

mod5<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    ytrue<-testdata[,5]
    mod<-glm(traindata$ConfirmedCases~
                  days_after_first_confirmedCases+
                  I(days_after_first_confirmedCases^2)+
                  tr.pwr(days_after_first_confirmedCases,12,2),
                 data=traindata,family=quasipoisson(link="log"))
  }else if(datatype=="fatalities"){
    ytrue<-testdata[,6]
    mod<-glm(traindata$Fatalities~
                  days_after_first_fatalities+
                  I(days_after_first_fatalities^2) +
                  tr.pwr(days_after_first_fatalities,2,2),
                 data=traindata,family=quasipoisson(link="log"))
  }
  pred<-round(predict(mod, newdata=testdata, type = "response"),0)
  mse<-MSE(y_pred=pred, y_true=ytrue)
  return(mse)
}
```

#### 3rd degree quasipoisson polynomial regression with truncated splines

```{r}
# 3rd degree quasipoisson polynomial regression with truncated splines 
mod6<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    ytrue<-testdata[,5]
    mod<-glm(traindata$ConfirmedCases~
                  days_after_first_confirmedCases+
                  I(days_after_first_confirmedCases^2)+
                   I(days_after_first_confirmedCases^3)+
                  tr.pwr(days_after_first_confirmedCases,12,3),
                 data=traindata,family=quasipoisson(link="log"))
  }else if(datatype=="fatalities"){
    ytrue<-testdata[,6]
    mod<-glm(traindata$Fatalities~
                  days_after_first_fatalities+
                  I(days_after_first_fatalities^2) +
                   I(days_after_first_fatalities^3) +
                  tr.pwr(days_after_first_fatalities,2,3),
                 data=traindata,family=quasipoisson(link="log"))
  }
  pred<-round(predict(mod, newdata=testdata, type = "response"),0)
  mse<-MSE(y_pred=pred, y_true=ytrue)
  return(mse)
}
```

#### 1st degree quasipoisson polynomial regression with B-splines

```{r}
# 1st degree quasipoisson regression with B-Spline
mod7<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    ytrue<-testdata[,5]
    mod<-glm(traindata$ConfirmedCases~
                  bs(days_after_first_confirmedCases,
                     degree=1,knots=28,Boundary.knots=c(1,82)),
                 data=traindata,family=quasipoisson(link="log"))
  }else if(datatype=="fatalities"){
    ytrue<-testdata[,6]
    mod<-glm(traindata$Fatalities~
                  bs(days_after_first_fatalities,
                     deg=1,knots=2,Boundary.knots=c(1,82)),
                 data=traindata,family=quasipoisson(link="log"))
  }
  pred<-round(predict(mod, newdata=testdata, type = "response"),0)
  mse<-MSE(y_pred=pred, y_true=ytrue)
  return(mse)
}
```

#### linear regression:

```{r}
# linear regression 
mod8<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    ytrue<-testdata[,5]
    mod<-lm(traindata$ConfirmedCases~days_after_first_confirmedCases+Province_State,data=traindata)
  }else if(datatype=="fatalities"){
    ytrue<-testdata[,6]
    mod<-lm(traindata$Fatalities~days_after_first_fatalities+Province_State,data=traindata)
  }
  pred<-round(predict(mod, newdata=testdata),0)
  mse<-MSE(y_pred=pred, y_true=ytrue)
  return(round(mse,2))
}
```

#### linear regression with log(x):

```{r}
# linear regression with log(x)
mod9<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    ytrue<-testdata[,5]
    mod<-lm(traindata$ConfirmedCases~log(days_after_first_confirmedCases)+
                   Province_State,data=traindata)
  }else if(datatype=="fatalities"){
    ytrue<-testdata[,6]
    mod<-lm(traindata$Fatalities~log(days_after_first_fatalities)+
                   Province_State,data=traindata)
  }
  pred<-round(predict(mod, newdata=testdata),0)
  mse<-MSE(y_pred=pred, y_true=ytrue)
  return(round(mse,2))
}
```

#### 2nd degree linear polynomial regression: 

```{r}
# 2nd degree linear polynomial regression 
mod10<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    ytrue<-testdata[,5]
    mod<-lm(traindata$ConfirmedCases~
                  days_after_first_confirmedCases +
                  I(days_after_first_confirmedCases^2),
                 data=traindata)
  }else if(datatype=="fatalities"){
    ytrue<-testdata[,6]
    mod<-lm(traindata$Fatalities~
                 days_after_first_fatalities+
                 I(days_after_first_fatalities^2),
                 data=traindata)
  }
  pred<-round(predict(mod, newdata=testdata),0)
  mse<-MSE(y_pred=pred, y_true=ytrue)
  return(mse)
}
```

#### 3rd degree linear polynomial regression: 

```{r}
# 3rd degree linear polynomial regression 
mod11<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    ytrue<-testdata[,5]
    mod<-lm(traindata$ConfirmedCases~
                  days_after_first_confirmedCases +
                  I(days_after_first_confirmedCases^2)+
                  I(days_after_first_confirmedCases^3),
                 data=traindata)
  }else if(datatype=="fatalities"){
    ytrue<-testdata[,6]
    mod<-lm(traindata$Fatalities~
                 days_after_first_fatalities+
                 I(days_after_first_fatalities^2)+
                 I(days_after_first_fatalities^3),
                 data=traindata)
  }
  pred<-round(predict(mod, newdata=testdata),0)
  mse<-MSE(y_pred=pred, y_true=ytrue)
  return(mse)
}
```

#### 2nd degree linear polynomial regression with truncated splines:

```{r}
# 2nd degree linear polynomial regression with truncated splines 
mod12<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    ytrue<-testdata[,5]
    mod<-lm(traindata$ConfirmedCases~
                  days_after_first_confirmedCases+
                  I(days_after_first_confirmedCases^2)+
                  tr.pwr(days_after_first_confirmedCases,32,2),
                 data=traindata)
  }else if(datatype=="fatalities"){
    ytrue<-testdata[,6]
    mod<-lm(traindata$Fatalities~
                  days_after_first_fatalities+
                  I(days_after_first_fatalities^2) +
                  tr.pwr(days_after_first_fatalities,2,2),
                 data=traindata)
  }
  pred<-round(predict(mod, newdata=testdata),0)
  mse<-MSE(y_pred=pred, y_true=ytrue)
  return(mse)
}
```

#### 3rd degree linear polynomial regression with truncated splines

```{r}
# 3rd degree linear polynomial regression with truncated splines 
mod13<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    ytrue<-testdata[,5]
    mod<-lm(traindata$ConfirmedCases~
                  days_after_first_confirmedCases+
                  I(days_after_first_confirmedCases^2)+
                   I(days_after_first_confirmedCases^3)+
                  tr.pwr(days_after_first_confirmedCases,12,3),
                 data=traindata)
  }else if(datatype=="fatalities"){
    ytrue<-testdata[,6]
    mod<-lm(traindata$Fatalities~
                  days_after_first_fatalities+
                  I(days_after_first_fatalities^2) +
                   I(days_after_first_fatalities^3) +
                  tr.pwr(days_after_first_fatalities,2,3),
                 data=traindata)
  }
  pred<-round(predict(mod, newdata=testdata),0)
  mse<-MSE(y_pred=pred, y_true=ytrue)
  return(mse)
}
```

#### 1st degree linear polynomial regression with B-splines

```{r}
# 1st degree linear regression with B-Spline
mod14<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    ytrue<-testdata[,5]
    mod<-lm(traindata$ConfirmedCases~
                  bs(days_after_first_confirmedCases,
                     degree=1,knots=28,Boundary.knots=c(1,82)),
                 data=traindata)
  }else if(datatype=="fatalities"){
    ytrue<-testdata[,6]
    mod<-lm(traindata$Fatalities~
                  bs(days_after_first_fatalities,
                     deg=1,knots=2,Boundary.knots=c(1,82)),
                 data=traindata)
  }
  pred<-round(predict(mod, newdata=testdata),0)
  mse<-MSE(y_pred=pred, y_true=ytrue)
  return(mse)
}
```

#### ARIMA

```{r}
mod15<-function(traindata,testdata,datatype){
  if (datatype=="confirmedcases"){
    mod_c_arima<-auto.arima(traindata$ConfirmedCases)
    pred_c<-round(as.data.frame(forecast(mod_c_arima,nrow(testdata)))[,1],0)
    mse<-MSE(y_pred=pred_c, y_true = testdata$ConfirmedCases)
  } else if (datatype=="fatalities"){
    mod_f_arima<-auto.arima(traindata$Fatalities)
    pred_f<-round(as.data.frame(forecast(mod_f_arima,nrow(testdata)))[,1],0)
    mse<-MSE(y_pred=pred_f, y_true = testdata$Fatalities)
  }
  return (mse)
}
```


```{r}
mse_dataframe[1,]<-c("quasipoisson logistic regression with x","N",
                    mod1(train_canada,test_canada,"confirmedcases"),
                    mod1(train_canada,test_canada,"fatalities"))
mse_dataframe[2,]<-c("quasipoisson logistic regression with log(x)","N",
                     mod2(train_canada,test_canada,"confirmedcases"),
                     mod2(train_canada,test_canada,"fatalities"))
mse_dataframe[3,]<-c("2nd degree quasipoisson polynomial regression","Y",
                     mse_by_province_canada(mod3,"confirmedcases"),
                     mse_by_province_canada(mod3,"fatalities"))
mse_dataframe[4,]<-c("3rd degree quasipoisson polynomial regression","Y",
                     mse_by_province_canada(mod4,"confirmedcases"),
                     mse_by_province_canada(mod4,"fatalities"))
mse_dataframe[5,]<-c("2nd degree quasipoisson polynomial regression with truncated splines","Y",
                     mse_by_province_canada(mod5,"confirmedcases"),
                     mse_by_province_canada(mod5,"fatalities"))
mse_dataframe[6,]<-c("3rd degree quasipoisson polynomial regression with truncated splines","Y",
                     mse_by_province_canada(mod6,"confirmedcases"),
                     mse_by_province_canada(mod6,"fatalities"))
mse_dataframe[7,]<-c("1st degree quasipoisson regression with B-Spline","Y",
                     mse_by_province_canada(mod7,"confirmedcases"),
                     mse_by_province_canada(mod7,"fatalities"))
mse_dataframe[8,]<-c("linear regression with x","N",
                    mod8(train_canada,test_canada,"confirmedcases"),
                    mod8(train_canada,test_canada,"fatalities"))
mse_dataframe[9,]<-c("linear regression with log(x)","N",
                     mod9(train_canada,test_canada,"confirmedcases"),
                     mod9(train_canada,test_canada,"fatalities"))
mse_dataframe[10,]<-c("2nd degree linear polynomial regression","Y",
                     mse_by_province_canada(mod10,"confirmedcases"),
                     mse_by_province_canada(mod10,"fatalities"))
mse_dataframe[11,]<-c("3rd degree linear polynomial regression","Y",
                     mse_by_province_canada(mod11,"confirmedcases"),
                     mse_by_province_canada(mod11,"fatalities"))
mse_dataframe[12,]<-c("2nd degree linear polynomial regression with truncated splines","Y",
                     mse_by_province_canada(mod12,"confirmedcases"),
                     mse_by_province_canada(mod12,"fatalities"))
mse_dataframe[13,]<-c("3rd degree linear polynomial regression with truncated splines","Y",
                     mse_by_province_canada(mod13,"confirmedcases"),
                     mse_by_province_canada(mod13,"fatalities"))
mse_dataframe[14,]<-c("1st degree linear regression with B-Spline","Y",
                     mse_by_province_canada(mod14,"confirmedcases"),
                     mse_by_province_canada(mod14,"fatalities"))
mse_dataframe[15,]<-c("arima","Y",
                     mse_by_province_canada(mod15,"confirmedcases"),
                     mse_by_province_canada(mod15,"fatalities"))
mse_dataframe
write.csv(mse_dataframe,file="mse.csv",quote=F,row.names = F)
```

### choosing methods: construct predictive models

confirmedcases: ARIMA


```{r}
# confirmedcases
confirmedcases_arima<-function(dataname){
  province_name<-as.character(unique(dataname$Province_State))
  confirmedcases_arimamod<-vector(mode = "list", length =12)
  for (i in 1:length(province_name)){
    province_train<-filter(dataname,Province_State==province_name[i])
    confirmedcases_arimamod[[i]]<-auto.arima(province_train$ConfirmedCases)
  }
  return(confirmedcases_arimamod)
}
confirmedcases_final_mod<-confirmedcases_arima(data_canada)
```


fatalities: quasipoisson logistic regression with log(x)

```{r}
# fatalities
fatalities_quasilog<-function(dataname){
  fatalities_quasilogmod<-vector(mode = "list", length =1)
  fatalities_quasilogmod[[1]]<-glm(Fatalities~
                  log(days_after_first_fatalities)+
                  Province_State,
                  data=dataname,family=quasipoisson(link="log"))
  return(fatalities_quasilogmod)
}
fatalities_final_mod<-fatalities_quasilog(data_canada)
```

### Prediction

```{r}
# confirmedcases
pred_confirmedcases<-function(dataname,preddays){
  province_name<-as.character(unique(dataname$Province_State))
  testdata<-data.frame(
    "Province_State"=rep(province_name,rep(preddays,length(province_name))),
    "Date"=rep(max(dataname$Date)+1:preddays,length(province_name)),
    "Pred_ConfirmedCases"=0)
  confirmedcases_final_mod<-confirmedcases_arima(dataname)
  pred<-numeric(0)
  for (i in 1:length(province_name)){
    pred_pro<-round(as.data.frame(forecast(confirmedcases_final_mod[[i]],preddays))[,1],0)
    pred<-c(pred,pred_pro)
  }
  pred[pred<0]<-0
  testdata$Pred_ConfirmedCases<-pred
  return(testdata)
}
dataframe_pred_confirmedcases<-pred_confirmedcases(data_canada,50)
# plot
national_pred_confirmedcases<-aggregate(Pred_ConfirmedCases~Date,dataframe_pred_confirmedcases,sum)
ts.plot(as.ts(national_pred_confirmedcases$Pred_ConfirmedCases))
```






```{r}
# fatalities
pred_fatalities<-function(dataname,preddays){
  province_name<-as.character(unique(dataname$Province_State))
  testdata<-data.frame(
    "Province_State"=rep(province_name,rep(preddays,length(province_name))),
    "Date"=rep(max(dataname$Date)+1:preddays,length(province_name)),
    "Pred_Fatalities"=0)
  temps<-numeric(0)
  for (i in 1:length(province_name)){
    temps<-c(temps,max(filter(dataname,Province_State==province_name[i])$days_after_first_fatalities)+1:preddays)
  }
  testdata$days_after_first_fatalities<-temps
  pred<-round(predict(fatalities_quasilog(dataname)[[1]], newdata = testdata,type="response"),0)
  pred[pred<0]<-0
  testdata$Pred_Fatalities<-pred
  return(testdata)
}
dataframe_pred_fatalities<-pred_fatalities(data_canada,50)
# plot
national_pred_fatalities<-aggregate(Pred_Fatalities~Date,dataframe_pred_fatalities,sum)
ts.plot(as.ts(national_pred_fatalities$Pred_Fatalities))
```

```{r}
plot1data<-cbind("Pred_ConfirmedCases"=dataframe_pred_confirmedcases[dataframe_pred_confirmedcases$Date=="2020-05-31	",c(3)],"Pred_Fatalities"=dataframe_pred_fatalities[dataframe_pred_fatalities$Date=="2020-05-31	",c(3)])
plot1data<-t(as.matrix(plot1data))
barplot(plot1data,col = c("red","black"),beside = TRUE)
```

```{r fig.width=6,fig.height=4}
datapart1<-data_canada[,c(2,4,5,6)]
datapart2<-cbind(dataframe_pred_confirmedcases[,c(1,2,3)],dataframe_pred_fatalities[,c(3)])
names(datapart2)<-c("Province_State","Date","ConfirmedCases","Fatalities")
plotdata2<-rbind(datapart1,datapart2)

# Time Series of Confirmed Cases in Canda From 2020-01.22 to 2020.05.31
province<-plotdata2 %>%
  group_split(Province_State)
province_name<-numeric(12)
for (i in 1:12){
    assign(paste0("province",i),as.ts(province[[i]]$ConfirmedCases))
    province_name[i]<-as.character(province[[i]]$Province_State[1])
}

color<-rainbow(12)
par(cex.main = 0.8)
ts.plot(province1,province2,province3,province4,province5,province6,province7,province8,province9,province10,province11,province12, col = color,main="Time Series of Confirmed Cases in Canda From 2020.01.22 to 2020.05.31")
legend("topleft", legend=province_name,lty=1, col=color,cex=0.5)
```

```{r fig.width=6,fig.height=4}
# Time Series of Fatalities in Canda From 2020-01.22 to 2020.05.31
province<-plotdata2 %>%
  group_split(Province_State)
province_name<-numeric(12)
for (i in 1:12){
    assign(paste0("province",i),as.ts(province[[i]]$Fatalities,start=c(2020,1,22),frequency=1))
    province_name[i]<-as.character(province[[i]]$Province_State[1])
}
# plot every provinces on the same plot
color<-rainbow(12)
par(cex.main = 0.8)
ts.plot(province1,province2,province3,province4,province5,province6,province7,province8,province9,province10,province11,province12, col = color,main="Time Series of Fatalities in Canda From 2020.01.22 to 2020.05.31")
legend("topleft", legend=province_name,lty=1, col=color,cex=0.5)
```



```{r include=FALSE}
write.csv(plotdata2,file="pred.csv",quote=F,row.names = F)
```


